---
title: "T-Test Problem"
author: "Arvin bowens"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_O$ : There is no difference in average years of education between those who voted   and those who didnt vote.  
$H_A$ :There is a difference in average years of education between those and did not.  
 
## graffical summary 


## Box plot
```{r}
plot(EDUC~VOTE12, data=Ourdata)
```
 
 It appars that the average years of education is about or same  for both groups.
 
## Numerical summary

```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```

## Inference test


```{r}
t.test(EDUC~VOTE12, data=Ourdata)
```

## conclusion
The p-value from the t-test is 0.005, this less than 0.05, so we   reject the null hypothesis and conclude we have evidence that   there is a difference between the average years of education of   those who voted in 2012 and those who didnt vote.  

  
 
 